Thermal reactionomes reveal divergent responses to thermal extremes in warm

### 2015-04-28 doc/ApTranscriptome_manuscript.Rmd
Added paragraph from SHC about common garden approach.

>>>>

## Common Garden Design

Ideally, genetically-based variation in gene expression profiles would be identified by comparing individuals completely reared under common-garden conditions to eliminate environmental variation experienced either as adults or during development. However, *Aphaenogaster* colonies are long-lived, cannot be bred under laboratory conditions, and do not achieve complete turnover of the workforce for at least a year or longer. Thus, as is commonly done with other long-lived organisms [@barshis2013, ], we exposed both colonies to common-garden rearing conditions for three months to fully acclimate adult workers to common temperatures. Over this time, roughly 1-2 cohorts of new  workers are expected to join the workforce (~1/3 of the total), such that the workers sampled for thermal traits and gene expression are likely to have included a mix of adult-acclimated and fully lab-reared individuals.
